{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-08-19 abstract.tex
finished complete draft, needs extension review

Reliable estimates of ecosystem metabolism depend on measures of \ac{DO} flux that are dominated by biological processes.  Long-term time series of \ac{DO} measurements may include variation related to both biological and physical processses such that the use of observed data may be insufficient in many examples.  Statistical modelling techniques that quantify variation in \ac{DO} over time and tidal changes have the potential to isolate biological signals in \ac{DO} variation to more accurately estimate metabolism.  We used a simulation approach to create an observed \ac{DO} time series as the summation of diel variation.  A weighted regression method that estimates \ac{DO} as a function of time and tidal height was used to normalize, or detide, the predicted \ac{DO} signal.  Comparisons of detided estimates with the known, simulated biological \ac{DO} signal suggested the method accurately and precisely removed varation attributed to tidal advection.  Extension of the method to four case studies provided a proof of concept illustrating the method could be useful for \textit{in situe} data. We provide a detailed discussion on use of the method for improving certainty in evaluation of \ac{DO} measurements from sites with strong tidal influences.  Moreover, we propose that the method will greatly expand use of the open-water method for estimating ecosystem metaoblism given that the approach can provide robust estimates of \ac{DO} values that are independent of tidal advection.  This could facilitate the use of shorter deployment periods for water quality monitors or incomplete time series given that known biases related to water movement could be removed with weighted regression.

>>>>

Reliable estimates of ecosystem metabolism depend on measures of \ac{DO} flux that are dominated by biological processes.  Long-term time series of \ac{DO} measurements may include variation related to both biological and physical processses such that the use of observed data may be insufficient or even misleading in some examples.  Statistical modelling techniques that dynamically quantify variation in \ac{DO} over time and tidal changes have the potential to isolate biological signals in \ac{DO} variation to more accurately estimate metabolism.  A weighted regression method that estimates \ac{DO} as a function of time and tidal height was developed to normalize, or detide, the predicted \ac{DO} signal to remove the influence of physical advection on metabolism estimates.  First, a simulation approach was used to create multiple \ac{DO} time series with known additive components of biological and physical variation on different periods.  Comparisons of detided estimates with the known, simulated biological component of the \ac{DO} signal suggested the method accurately and precisely removed varation attributed to tidal advection.  Extension of the method to four case studies provided a proof of concept illustrating the method could be useful for real-world applications. We provide a detailed discussion on use of the method for improving certainty in evaluation of \ac{DO} measurements from sites with strong tidal influences.  Moreover, we propose that the method could expand use of the open-water method for estimating ecosystem metaoblism in estuaries given that the approach can produce robust estimates of \ac{DO} values that are independent of tidal advection.  In particular, this could facilitate the use of shorter deployment periods for water quality monitors or incomplete time series given that known biases related to water movement could be removed with weighted regression.

### 2014-08-19 comments.Rnw
finished complete draft, needs extension review

To date, only a few analyses have focused on systematic comparisons of estuarine metabolism estimates across broad spatial and temporal scales.  Exceptions include \citet{Caffrey03}, \citet{Caffrey04}, and \citet{Caffrey13}.

>>>>

Results from the simulations and case studies suggested that weighted regression is a practical approach for detiding \ac{DO} time series to remove the effects of physical advection on estimates of ecosystem metabolism.  However, application of the method may only be appropriate under specific situations.  The case studies were chosen based on the expected influence of tidal variaiton given the relatively high proportion of metabolism estimates that were anomalous and the strength of correlation between the observed \ac{DO} time series and tidal height.  The results for Elkhorn Slough were cause for concern given that the detided metabolism estimates were substantially reduced compared to those from the observed \ac{DO} time series.  Although the correlation of \ac{DO} and tidal height was reduced, in addition to a reduction of anomalous estimates, the relative change in mean metabolism before and after detiding was unusually large.  The detiding results are highly sensitive to changes in the window widths, particularly the hour window.  Further investigation of the effects of different window widths on the metabolism estimates for Elkhorn Slough were unable to produce satisfactory results such that the metabolism estimates were significantly lower in all cases.  This suggests that the weighted regression was removing variation in the observed \ac{DO} related to both tidal changes and metabolic components.

The results for Elkhorn Slough provide an example that emphasizes the need for restraint in applying weighted regression.  Because the true biological \ac{DO} signal is not known, no single measure can provide a true representation of the effectiveness of weighted regression.  Accordingly, we propose a precautionary approach that emphasizes application of the method following a set of conditions and steps.  First, weighted regression should only be applied at macrotidal sites and if there is strong evidence of the confounding effects of tidal advection.  The occurrence of anomalous estimates alone may not be sufficient for justifying use of the method.  A simple scatterplot of observed \ac{DO} versus tide height should indicate a strong correlation, in addition to clear visual patterns of tide change on \ac{DO}.  Second, significant changes in mean metabolic rates before and after detiding warrants a more comprehensive application of the method, with attention on specific window widths.  Changes in mean annual rates are of particular concern, which suggest that the method has reduced both physical and biological variation in the \ac{DO} signal.  Third, optimal results may be those that indicate a reduction of anomalous estimates, reduction in daily variation of production and respiration, and a reduction of the correlation between \ac{DO} and tide.  In general, a pragmatic approach is emphasized such that results based on detided estimates should be evaluated for the preservation of diel variation while exhibiting minimal changes with the tide.  Such an approach will support more accurate estimates of ecosystem metabolism that fulfill assumptions of the open-water method.

% caution when mean changes

### 2014-08-19 discussion.Rnw
finished complete draft, needs extension review

The performance metrics used to evaluate weighted regression with the case studies indicated that detiding improved estimates of ecosystem metabolism.  Correlations of metabolism estimates with tidal height changes suggested that detiding produced less biased estimates, although trends were not particularly clear as correlations were reduced in some cases (Sapelo Island) or reversed in others (Padilla Bay).  However, correlations of net metabolism estimates were reduced in all cases.  Tidal height changes directly affect the measured rate of change of oxygen, which is an integrated measure of both production and respiration (\cref{metrate}).  An evaluation of tidal height change with production or respiration may be misleading since each represents a unique portion of the diel \aC{DO} signal that is directly affected by tidal variation.  Regardless, the proportion of anomalous metabolism estimates was reduced by detiding for all case studies, although this measure may also be an incomplete indication of the combined effects of tidal variation.  Negative production and positive respiration estimates suggest assumptions of the open-water method are violated \citep{Needoba12}.  However, `normal' estimates (positive production and negative respiration) may still include a significant source of bias from physical advection by providing over-estimates of true values.  \citet{Nidzieko14} observed that net metabolism at Elkhorn Slough was more often heterotrophic during maximum spring tides that occurred at nighttime, as a substantially larger area of salt marsh was inundated leading to higher respiration estimates.  Although this result supports our general conclusions, a broader discusion regarding whether or not this represents a bias in metabolism from physical advection may be needed.

A strength of the weighted regression approach is the lack of assumptions that are required for relationships between \ac{DO} and tidal variation over time.

% emphasis on improvement over other methods

% new insights, reinterpretation of existing data

\begin{comment}

- degree to which method meets need defined in introduction
  -sims
  -case studies

- potential for new insight
- whether existing data should be reinterpreted
  -potentially

what did I find?

- simulations work well
- DO time series were detided for case studies, show comvincingly
  - corrs w/ tide and moving correlation/beta plots?, DO and DOF are different
- metab ests for case studies were generally unchanged
  - related to the fact that metab is daily integrated that averages out
  - but show PDB example, really a major issue when the stars align (tide always going out during the day etc. more of a problem for strong diurnal tides, method was useful for this example
- method should not be broadly used to fix `anomalous' metab estimates, these are likely not caused by tides unless a case like PDB
- method should be used to detide DO, useful in that regard

 Assumptions of relationships between variables are not necessary using this adaptive weighting scheme given that the method has the ability to interpret statistical relationships without prior knowledge.

weighted regression approach is very useful because DO and tide are cyclical and the interaction varies depending on whether they are in or out of phase.  the approach is adaptive and does not require the user to identify the relationship a priori, a relationship that is comlicated by the additive combination of multiple sine waves.

make note that a non-moving window approach could work only if the relationship of time, tide, DO is constant throughout the time series.  For example, regression of do w/ tide before/after detiding using a non-weighted approach detided the whole series but had variable success by month,  where weighted approach detided each month completley.  Simulations did not test for this, although this was apparent with the case studies.

why not just fourier transform or hi/lo pass filters?  See Needobe et al. chapter and Batt and Carpenter 2012  for examples of this, need to the pros/cons of each technique, we assume that noise not related to tidal advection is DO from biology

air-sea gas exchange, how might this influence results

Most bias may be expected during the summer...
\end{comment}

>>>>

The performance metrics used to evaluate weighted regression with the case studies indicated that detiding improved estimates of ecosystem metabolism.  Correlations of metabolism estimates with tidal height changes suggested that detiding produced less biased estimates, although trends were not particularly clear as correlations were reduced in some cases (Sapelo Island) or reversed in others (Padilla Bay).  However, correlations of net metabolism estimates were reduced in all cases.  Tidal height changes directly affect the measured rate of change of oxygen, which is an integrated measure of both production and respiration (\cref{metrate}).  An evaluation of tidal height change with production or respiration may be misleading since each represents a unique portion of the diel \ac{DO} signal that is directly affected by tidal variation.  Regardless, the proportion of anomalous metabolism estimates was reduced by detiding for all case studies, although this measure may also be an incomplete indication of the combined effects of tidal variation.  Negative production and positive respiration estimates suggest assumptions of the open-water method are violated \citep{Needoba12}, whereas `normal' estimates (positive production and negative respiration) may still include a significant source of bias from physical advection by providing over-estimates of true values.  For example, \citet{Nidzieko14} observed that net metabolism at Elkhorn Slough was more often heterotrophic during maximum spring tides that occurred at nighttime, as a substantially larger area of salt marsh was inundated leading to higher respiration estimates.  Although this result supports our general conclusions, a broader discusion regarding whether or not this represents a bias in metabolism from physical advection may be needed.

A strength of the weighted regression approach is the lack of assumptions for describing the relationships between \ac{DO} and tidal variation over time.  Although the functional form of the model is a simple linear regression with two explanatory variables (\cref{funform}), the moving window approach combined with the adaptive weighting scheme allows for quantification of complex tidal effects that may not be possible using alternative approaches.  For example, \citet{Batt12} described the use of a moving window or Kalman filter to improve estimates of ecosystem metabolism in lakes.  The approach minimizes the influences of process and observation uncertainty on observed \ac{DO} time series, which the authors assume is the product of spatial variation not related to metabolism.  Such an approach may be useful for estuaries if process and observation uncertainty are the primary sources of variation, whereas the weighted regression approach would be more appropriate if tidal advection is considered an additional confounding factor of the diel \ac{DO} component.  Additionally, results from the case studies illustrate the ability of the weighted regression approach to model changes in the relationships between tidal change and \ac{DO} over time.  Results for Padilla Bay and Rookery Bay suggested that detiding had the largest effect during the summer, whereas the results for cooler months were not significantly different from the observed.  The weighted regression method produced detided time series that accommodated seasonal variation in \ac{DO} conditional on tidal height change, whereas moving window filters would likely not have characterized these dynamic relationships.

### 2014-08-19 swmp_noise.Rnw
started discussion, almost done...
finished complete draft, needs extension review

%%%%%%
% comments and recs
\section{Comments and recommendations}

@@

% example from RKBMB
\centering\vspace*{\fill}
<<case_ex1, cache = T, fig.height = 6.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of daily mean metabolism (top) and continuous \\ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$) is on the bottom plot. Results are for the Rookery Bay station for twenty days in July, 2012 using a weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.'>>=
######
# RKBMB example

@@

# reassign factor labels
to_plo$value <- factor(to_plo$value, levels = c('01', '02', '03', '04',
  '05', '06', '07', '08', '09', '10', '11', '12', 'F', 'Sp', 'Su', 'W'), 
  labels = c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',' 12',
    'F', 'Sp', 'Su', 'W')
  )
to_plo$var <- factor(to_plo$var, levels = c('Pg', 'Rt', 'NEM'), 
  labels = c('Pg', 'Rt', 'NEM'))
to_plo$sub_var <- factor(to_plo$sub_var, levels = c('dtd', 'obs'), 
  labels = c('Detided', 'Observed'))
to_plo$L1 <- gsub('_wtreg_[0-9]*.RData$', '', to_plo$L1)
to_plo$L1 <- factor(to_plo$L1, 
  levels = c('ELKVM', 'PDBBY', 'RKBMB', 'SAPDC'),
  labels = c('Elkhorn Slough', 'Padilla Bay', 'Rookery Bay', 
    'Sapelo Island')
  )

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \\ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regressions with a window of thirty days and tidal height proportion of one.'

>>>>

%%%%%%
% comments and recs
\section{Comments and recommendations}
<<comments, child = 'comments.Rnw'>>=
@

@@

% example from RKBMB
\centering\vspace*{\fill}
<<case_ex1, cache = T, fig.height = 6.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of daily mean metabolism (top) and continuous \\ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$) is on the bottom plot. Results are for the Rookery Bay station for twenty days in August, 2012 using a weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.'>>=
######
# RKBMB example

@@

# reassign factor labels
to_plo$value <- factor(to_plo$value, levels = c('01', '02', '03', '04',
  '05', '06', '07', '08', '09', '10', '11', '12', 'W', 'Sp', 'Su', 'F'), 
  labels = c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',' 12',
    'W', 'Sp', 'Su', 'F')
  )
to_plo$var <- factor(to_plo$var, levels = c('Pg', 'Rt', 'NEM'), 
  labels = c('Pg', 'Rt', 'NEM'))
to_plo$sub_var <- factor(to_plo$sub_var, levels = c('dtd', 'obs'), 
  labels = c('Detided', 'Observed'))
to_plo$L1 <- gsub('_wtreg_[0-9]*.RData$', '', to_plo$L1)
to_plo$L1 <- factor(to_plo$L1, 
  levels = c('ELKVM', 'PDBBY', 'RKBMB', 'SAPDC'),
  labels = c('Elkhorn Slough', 'Padilla Bay', 'Rookery Bay', 
    'Sapelo Island')
  )

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \\ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.'

### 2014-08-19 swmp_noise.tex
finished complete draft, needs extension review

The observed and detided daily estimates were averaged by month and season (Fall, Spring, Summer, and Winter) for each case study to evaluate differences in mean metabolism estimates as a basis for evaluating aggregation effects on different periods of observation (\cref{fig:metab_sum1,fig:metab_sum2}).  Interestingly, estimates of net metabolism were similar regardless of the period of observation for which values were aggregated.  This suggests that averaged net metabolism estimates based on observed \ac{DO} time series will produce unbiased results at relatively short periods of observation (e.g., monthly), although note that substantial within-period variability may be observed compared to using a detided \ac{DO} time series.  However, significant variation in aggregated production and respiration estimates for month and season was observed for each case study.  Detided production and respiration estimates exhibited seasonal and monthly variation that was more characteristic of expected trends with increases in metabolism during warmer months.  For example, production estimates based on observed \ac{DO} were substantially muted for both Padilla Bay (\cref{fig:metab_sum1}) and Rookery Bay (\cref{fig:metab_sum2}) during summer months, whereas values were significantly higher based on the detided data. Results for Elkhorn Slough were an exception such that seasonal variation in production and respiration were significantly reduced after detiding.  Regardless of trends, these results suggest that tidal variation can affect interpretations of metabolic trends that are based on aggregations of daily values, particularly those as short as one month.

@@

Comparisons between detided and biological \ac{DO} time series from the simulations indicated that adequate results can be obtained from the weighted regression for a range of characteristics of \ac{DO} time series, as well as half window widths used in the regression.  An examination of scenarios that produced abnormal results can provide additional insight into factors that affect the performance of weighted regression.  For example, poor performance was observed when the observation uncertainty ($\epsilon_{obs}$) was high and both process uncertainty ($\epsilon_{pro}$) and tidal advection ($DO_{adv}$) were low.  These examples represent time series with excessive random variation, no auto-correlation, and no tidal influence.  Poor performance is expected because the weighted regression models a non-existent tidal signal in a very noisy \ac{DO} time series.  These results were observed even for time series with a large diel component of the biological \ac{DO} signal, suggesting that the model will produce unreliable results in microtidal systems with high noise and no serial correlation.  From a practical perspective, weighted regression should not be applied to noisy time series if there not sufficient evidence to believe the variation is related to tidal changes.  Similarly, results with perfect or near-perfect correlations between detided and biological \ac{DO} time series were observed when observation uncertainy and tidal advection effects were not in the simulated time series.  Although there is no logical basis for applying weighted regression to such a time series, the results will not be misleading, as was the case for low tidal advection, high observation uncertainty, and low process uncertainty.

The performance metrics used to evaluate weighted regression with the case studies indicated that detiding improved estimates of ecosystem metabolism.  Correlations of metabolism estimates with tidal height changes suggested that detiding produced less biased estimates, although trends were not particularly clear as correlations were reduced in some cases (Sapelo Island) or reversed in others (Padilla Bay).  However, correlations of net metabolism estimates were reduced in all cases.  Tidal height changes directly affect the measured rate of change of oxygen, which is an integrated measure of both production and respiration (\cref{metrate}).  An evaluation of tidal height change with production or respiration may be misleading since each represents a unique portion of the diel \aC{DO} signal that is directly affected by tidal variation.  Regardless, the proportion of anomalous metabolism estimates was reduced by detiding for all case studies, although this measure may also be an incomplete indication of the combined effects of tidal variation.  Negative production and positive respiration estimates suggest assumptions of the open-water method are violated \citep{Needoba12}.  However, `normal' estimates (positive production and negative respiration) may still include a significant source of bias from physical advection by providing over-estimates of true values.  \citet{Nidzieko14} observed that net metabolism at Elkhorn Slough was more often heterotrophic during maximum spring tides that occurred at nighttime, as a substantially larger area of salt marsh was inundated leading to higher respiration estimates.  Although this result supports our general conclusions, a broader discusion regarding whether or not this represents a bias in metabolism from physical advection may be needed.

A strength of the weighted regression approach is the lack of assumptions that are required for relationships between \ac{DO} and tidal variation over time.

% emphasis on improvement over other methods

% new insights, reinterpretation of existing data

\begin{comment}

- degree to which method meets need defined in introduction
  -sims
  -case studies

- potential for new insight
- whether existing data should be reinterpreted
  -potentially

what did I find?

- simulations work well
- DO time series were detided for case studies, show comvincingly
  - corrs w/ tide and moving correlation/beta plots?, DO and DOF are different
- metab ests for case studies were generally unchanged
  - related to the fact that metab is daily integrated that averages out
  - but show PDB example, really a major issue when the stars align (tide always going out during the day etc. more of a problem for strong diurnal tides, method was useful for this example
- method should not be broadly used to fix `anomalous' metab estimates, these are likely not caused by tides unless a case like PDB
- method should be used to detide DO, useful in that regard

 Assumptions of relationships between variables are not necessary using this adaptive weighting scheme given that the method has the ability to interpret statistical relationships without prior knowledge.

weighted regression approach is very useful because DO and tide are cyclical and the interaction varies depending on whether they are in or out of phase.  the approach is adaptive and does not require the user to identify the relationship a priori, a relationship that is comlicated by the additive combination of multiple sine waves.

make note that a non-moving window approach could work only if the relationship of time, tide, DO is constant throughout the time series.  For example, regression of do w/ tide before/after detiding using a non-weighted approach detided the whole series but had variable success by month,  where weighted approach detided each month completley.  Simulations did not test for this, although this was apparent with the case studies.

why not just fourier transform or hi/lo pass filters?  See Needobe et al. chapter and Batt and Carpenter 2012  for examples of this, need to the pros/cons of each technique, we assume that noise not related to tidal advection is DO from biology

air-sea gas exchange, how might this influence results

Most bias may be expected during the summer...
\end{comment}

@@

\caption[Example of daily mean metabolism (top) and continuous \ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression]{Example of daily mean metabolism (top) and continuous \ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$) is on the bottom plot. Results are for the Rookery Bay station for twenty days in July, 2012 using a weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.\label{fig:case_ex1}}
\end{figure}

@@

% case study metabolism results, including perc anom
% latex.default(tab, file = "", rowlabel = "Site", insert.bottom = foot.val,      caption = cap.val, caption.loc = "top", rgroup = unique(to_tab$Site),      n.rgroup = rep(2, 4), cgroup = c("Pg\\textsuperscript{\\textit{a}}",          "Rt", "NEM"), n.cgroup = c(3, 3, 2), rowname = rows,      colheads = c(rep(c("Mean", "Std. Err.", "Anom"), 2), c("Mean",          "Std. Err.")), label = "tab:case_res") 
%
\begin{table}[!tbp]
\caption{Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regressions with a window of thirty days and tidal height proportion of one.\label{tab:case_res}} 
\begin{center}
\begin{tabular}{llllclllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Site}&\multicolumn{3}{c}{\bfseries Pg\textsuperscript{\textit{a}}}&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Rt}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NEM}\tabularnewline
\cline{2-4} \cline{6-8} \cline{10-11}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}\tabularnewline
\hline
{\bfseries ELKVM}&&&&&&&&&&\tabularnewline
~~Observed&8.14&0.67&0.19&&-8.19&0.69&0.21&&-0.05&0.16\tabularnewline
~~Detided&2.78&0.14&0.11&&-2.83&0.15&0.12&&-0.05&0.03\tabularnewline
\hline
{\bfseries PDBBY}&&&&&&&&&&\tabularnewline
~~Observed&5.95&0.69&0.22&&-5.90&0.74&0.19&& 0.05&0.22\tabularnewline
~~Detided&8.07&0.40&0.05&&-8.04&0.39&0.06&& 0.04&0.06\tabularnewline
\hline
{\bfseries RKBMB}&&&&&&&&&&\tabularnewline
~~Observed&3.02&0.14&0.09&&-3.62&0.15&0.08&&-0.60&0.06\tabularnewline
~~Detided&2.73&0.07&0.00&&-3.34&0.07&0.00&&-0.61&0.03\tabularnewline
\hline
{\bfseries SAPDC}&&&&&&&&&&\tabularnewline
~~Observed&4.89&0.23&0.13&&-6.04&0.25&0.11&&-1.16&0.09\tabularnewline
~~Detided&4.40&0.08&0.00&&-5.58&0.09&0.00&&-1.18&0.05\tabularnewline
\hline
\end{tabular}
\end{center}
\textsuperscript{\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism\end{table}

>>>>

The observed and detided daily estimates were averaged by month and season (Fall, Spring, Summer, and Winter) for each case study to evaluate differences in mean metabolism estimates as a basis for evaluating aggregation effects on different periods of observation (\cref{fig:metab_sum1,fig:metab_sum2}).  Interestingly, estimates of net metabolism were similar regardless of the period of observation for which values were aggregated.  This suggests that averaged net metabolism estimates based on observed \ac{DO} time series will produce unbiased results at relatively short periods of observation (e.g., monthly), although note that substantial within-period variability may be observed compared to using a detided \ac{DO} time series.  Significant variation in aggregated production and respiration estimates for month and season was observed for each case study.  Detided production and respiration estimates exhibited seasonal and monthly variation that was more characteristic of expected trends with increases in metabolism during warmer months.  For example, production estimates based on observed \ac{DO} were substantially muted for both Padilla Bay (\cref{fig:metab_sum1}) and Rookery Bay (\cref{fig:metab_sum2}) during summer months, whereas values were significantly higher based on the detided data. Results for Elkhorn Slough were an exception such that seasonal variation in production and respiration were significantly reduced after detiding.  Regardless of trends, these results suggest that tidal variation can affect interpretations of metabolic trends that are based on aggregations of daily values, particularly those as short as one month.

@@

Comparisons between detided and biological \ac{DO} time series from the simulations indicated that adequate results can be obtained from the weighted regression for a range of characteristics of \ac{DO} time series, as well as half window widths used in the regression.  An examination of scenarios that produced abnormal results can provide additional insight into factors that affect the performance of weighted regression.  For example, poor performance was observed when the observation uncertainty ($\epsilon_{obs}$) was high and both process uncertainty ($\epsilon_{pro}$) and tidal advection ($DO_{adv}$) were low.  These examples represent time series with excessive random variation, no auto-correlation, and no tidal influence.  Poor performance is expected because the weighted regression models a non-existent tidal signal in a very noisy \ac{DO} time series.  These results were observed even for time series with a large diel component of the biological \ac{DO} signal, suggesting that the model will produce unreliable results in microtidal systems with high noise and no serial correlation.  From a practical perspective, weighted regression should not be applied to noisy time series if there is not sufficient evidence to suggest the variation is related to tidal changes.  Similarly, results with perfect or near-perfect correlations between detided and biological \ac{DO} time series were observed when observation uncertainy and tidal advection effects were not in the simulated time series.  Although there is no logical basis for applying weighted regression to such a time series, the results will not be misleading, as was the case for low tidal advection, high observation uncertainty, and low process uncertainty.

The performance metrics used to evaluate weighted regression with the case studies indicated that detiding improved estimates of ecosystem metabolism.  Correlations of metabolism estimates with tidal height changes suggested that detiding produced less biased estimates, although trends were not particularly clear as correlations were reduced in some cases (Sapelo Island) or reversed in others (Padilla Bay).  However, correlations of net metabolism estimates were reduced in all cases.  Tidal height changes directly affect the measured rate of change of oxygen, which is an integrated measure of both production and respiration (\cref{metrate}).  An evaluation of tidal height change with production or respiration may be misleading since each represents a unique portion of the diel \ac{DO} signal that is directly affected by tidal variation.  Regardless, the proportion of anomalous metabolism estimates was reduced by detiding for all case studies, although this measure may also be an incomplete indication of the combined effects of tidal variation.  Negative production and positive respiration estimates suggest assumptions of the open-water method are violated \citep{Needoba12}, whereas `normal' estimates (positive production and negative respiration) may still include a significant source of bias from physical advection by providing over-estimates of true values.  For example, \citet{Nidzieko14} observed that net metabolism at Elkhorn Slough was more often heterotrophic during maximum spring tides that occurred at nighttime, as a substantially larger area of salt marsh was inundated leading to higher respiration estimates.  Although this result supports our general conclusions, a broader discusion regarding whether or not this represents a bias in metabolism from physical advection may be needed.

A strength of the weighted regression approach is the lack of assumptions for describing the relationships between \ac{DO} and tidal variation over time.  Although the functional form of the model is a simple linear regression with two explanatory variables (\cref{funform}), the moving window approach combined with the adaptive weighting scheme allows for quantification of complex tidal effects that may not be possible using alternative approaches.  For example, \citet{Batt12} described the use of a moving window or Kalman filter to improve estimates of ecosystem metabolism in lakes.  The approach minimizes the influences of process and observation uncertainty on observed \ac{DO} time series, which the authors assume is the product of spatial variation not related to metabolism.  Such an approach may be useful for estuaries if process and observation uncertainty are the primary sources of variation, whereas the weighted regression approach would be more appropriate if tidal advection is considered an additional confounding factor of the diel \ac{DO} component.  Additionally, results from the case studies illustrate the ability of the weighted regression approach to model changes in the relationships between tidal change and \ac{DO} over time.  Results for Padilla Bay and Rookery Bay suggested that detiding had the largest effect during the summer, whereas the results for cooler months were not significantly different from the observed.  The weighted regression method produced detided time series that accommodated seasonal variation in \ac{DO} conditional on tidal height change, whereas moving window filters would likely not have characterized these dynamic relationships.

@@

\caption[Example of daily mean metabolism (top) and continuous \ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression]{Example of daily mean metabolism (top) and continuous \ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$) is on the bottom plot. Results are for the Rookery Bay station for twenty days in August, 2012 using a weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.\label{fig:case_ex1}}
\end{figure}

@@

% case study metabolism results, including perc anom
% latex.default(tab, file = "", rowlabel = "Site", insert.bottom = foot.val,      caption = cap.val, caption.loc = "top", rgroup = unique(to_tab$Site),      n.rgroup = rep(2, 4), cgroup = c("Pg\\textsuperscript{\\textit{a}}",          "Rt", "NEM"), n.cgroup = c(3, 3, 2), rowname = rows,      colheads = c(rep(c("Mean", "Std. Err.", "Anom"), 2), c("Mean",          "Std. Err.")), label = "tab:case_res") 
%
\begin{table}[!tbp]
\caption{Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.\label{tab:case_res}} 
\begin{center}
\begin{tabular}{llllclllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Site}&\multicolumn{3}{c}{\bfseries Pg\textsuperscript{\textit{a}}}&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Rt}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NEM}\tabularnewline
\cline{2-4} \cline{6-8} \cline{10-11}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}&\multicolumn{1}{c}{Anom}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Std. Err.}\tabularnewline
\hline
{\bfseries ELKVM}&&&&&&&&&&\tabularnewline
~~Observed&8.14&0.67&0.19&&-8.19&0.69&0.21&&-0.05&0.16\tabularnewline
~~Detided&2.78&0.14&0.11&&-2.83&0.15&0.12&&-0.05&0.03\tabularnewline
\hline
{\bfseries PDBBY}&&&&&&&&&&\tabularnewline
~~Observed&5.95&0.69&0.22&&-5.90&0.74&0.19&& 0.05&0.22\tabularnewline
~~Detided&8.07&0.40&0.05&&-8.04&0.39&0.06&& 0.04&0.06\tabularnewline
\hline
{\bfseries RKBMB}&&&&&&&&&&\tabularnewline
~~Observed&3.02&0.14&0.09&&-3.62&0.15&0.08&&-0.60&0.06\tabularnewline
~~Detided&2.73&0.07&0.00&&-3.34&0.07&0.00&&-0.61&0.03\tabularnewline
\hline
{\bfseries SAPDC}&&&&&&&&&&\tabularnewline
~~Observed&4.89&0.23&0.13&&-6.04&0.25&0.11&&-1.16&0.09\tabularnewline
~~Detided&4.40&0.08&0.00&&-5.58&0.09&0.00&&-1.18&0.05\tabularnewline
\hline
\end{tabular}
\end{center}
\textsuperscript{\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism\end{table}
